---
title: "Week1 - EX1b"
author: "Severin Spring"
date: "30 September 2019"
output: html_document
---

Week 1 Exercise (part b):
1. Acquaint yourself with knitR PDF/HTML Rmarkdown documents [1].
2. Create an HTML document that samples 100 values from a log-normal
distribution (say, mu=1, sigma=.25); create a histogram of the
distribution and the distribution on the log scale; report the mean and
variance of the sample in line in the text. (In general, do not just dump
the R code and plots in the HTML document; break your exercises into
sections with headings, add some text and make it readable.


### Sample data (with seed)

```{r}
set.seed(42)
dat <- rlnorm(100, mean=1, sd= 0.25)
```


### Plots - lets look at the data

```{r}
plot(dat, ylab = 'values of sampled log-norm distribution')
hist(dat, xlab='value',  main='Histogram', col='blue')
hist(log(dat), xlab='log(value)', main='Histogram with log scale' , col='green')
```

### Simple EDA of our data

```{r}
m <- mean(dat)
v <- var(dat)
```
  
Rounded to the second decimal the mean (_m_) of the sampled log-norm distribution is `r round(m,2)` and the variance (_v_) `r round(v,2)`.
